Total Score

### 2023-01-23 src/MSAtotal_scores.Rmd
calculated total scores using weights from Owen and student weights

```{r}
# read in the data
category_score_data <- read_sheet(https://docs.google.com/spreadsheets/d/1zu6ta_gI5lF3l2RC5eE3BuUsywYg8gd6xcMfuTKb9Bk/edit#gid=852316062)

@@

>>>>

```{r}
# read in the data
real_estate_score_data <- read_sheet("https://docs.google.com/spreadsheets/d/1Ssmb7pUd4NFZocVp9C75SRMOV6tAJCCt0TjrCYBB8pY/edit#gid=1038418521") %>% 
  select(cbsa, real_estate_score)

rental_policy_score_data <- read_sheet("https://docs.google.com/spreadsheets/d/1nLpDhM88a3rEBDVK5RZlk2B6QuwVIwvsfE5HeBz0mLo/edit#gid=983090810") %>% 
  select(cbsa, landlord_score)

reopt_data <- read_sheet("https://docs.google.com/spreadsheets/d/1tPqpmS8JOeRyunEmSyFYPYwshKDGx54Z-MISgYO3wZE/edit#gid=1874679054") %>% 
  select(cbsa, city_msa, state, normalized_irr, inverted_n_total_co2, inverted_n_health_emissions_cost, normalized_annual_renewable)

climate_risk_data <- read_sheet("https://docs.google.com/spreadsheets/d/1HZCeNGf61RJ9GJs3cLJcl9aNpvmPMBF1Yoss2fytltc/edit#gid=2045475301") %>% 
  select(cbsa, normalized_inverted_climate_risk)

@@

```{r}
criteria_all <- real_estate_score_data %>% 
  inner_join(rental_policy_score_data)  %>% 
  inner_join(reopt_data) %>% 
  inner_join(climate_risk_data)
```

```{r}
# weight criteria for Owen
criteria_weights_owen <- c(0.37, 0.12, 0.22, 0.07, 0.0, 0.07, 0.15)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_owen = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$total_score_owen[i] = weighted.mean(cbsa_data, criteria_weights_owen)
}

```{r}
# weight criteria for students
criteria_weights_students <- c(0.21, 0.0, 0.12, 0.17, 0.16, 0.17, 0.17)

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_students = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

size <- dim(criteria_all)
for (i in 1:size[1]) {
  cbsa_data <- c(criteria_all$real_estate_score[i],
                criteria_all$landlord_score[i],
                 criteria_all$normalized_irr[i],
                 criteria_all$inverted_n_total_co2[i],
                criteria_all$inverted_n_health_emissions_cost[i],
                criteria_all$normalized_annual_renewable[i],
                criteria_all$normalized_inverted_climate_risk[i]
                  )
  criteria_all$total_score_students[i] = weighted.mean(cbsa_data, criteria_weights_students)
}

```{r}
sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0")
```
